Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2021-03-10 assets/waveform_subband.tex
:art: Update labels
:art: Update layout
:construction: Update manuscript

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,3.503in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	2.82172700965795\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{$s_I$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	0.000289213065829642\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{$s_P$}

@@

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,2.747in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.295470946033806\\
2	2.78041553969328\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	6.88515292983531e-06\\
2	7.11243494475005e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,1.992in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.00886602819700381\\
2	0.0237787230194659\\
3	0.108070855596065\\
4	1.1713310546201\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.633626542983812\\
2	0.829836144183102\\
3	0.976226628588797\\
4	1.35354289111746\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,1.237in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.00167790645812327\\
2	0.00228016548777977\\
3	0.00318742185439004\\
4	0.00462726511721075\\
5	0.00716743728878421\\
6	0.0129273763723776\\
7	0.0308460700090715\\
8	0.115533318647694\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.603245855871981\\
2	0.755456602981771\\
3	0.858512489463287\\
4	0.953124795407537\\
5	1.02704466315581\\
6	1.08592420449446\\
7	1.13090925633169\\
8	1.18526539633296\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,0.481in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.000617491691008369\\
2	0.000717776254822589\\
3	0.000835285279992789\\
4	0.000979591082427033\\
5	0.00115487030006212\\
6	0.00136293515999463\\
7	0.00161619354701616\\
8	0.00191279748068678\\
9	0.00227218304658774\\
10	0.0026908090305821\\
11	0.00319938829308565\\
12	0.00381122202979217\\
13	0.00474535479665619\\
14	0.00756353464992525\\
15	0.017474797658002\\
16	0.0547436973724798\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.418853266349202\\
2	0.478839773751748\\
3	0.529812149718329\\
4	0.573539152412764\\
5	0.611663102441733\\
6	0.642886720358442\\
7	0.677359347479036\\
8	0.701877932539796\\
9	0.729554340449397\\
10	0.748421821359951\\
11	0.768367609874633\\
12	0.782658242865203\\
13	0.796571330906253\\
14	0.806933582871612\\
15	0.818312174451126\\
16	0.833414484583038\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

>>>>

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,3.503in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	2.82172700965795\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{$\boldsymbol{s}_{\mathrm{I}}$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	0.000289213065829642\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{$\boldsymbol{s}_{\mathrm{P}}$}

@@

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,2.747in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.295470946033806\\
2	2.78041553969328\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	6.88515292983531e-06\\
2	7.11243494475005e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,1.992in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.00886602819700381\\
2	0.0237787230194659\\
3	0.108070855596065\\
4	1.1713310546201\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.633626542983812\\
2	0.829836144183102\\
3	0.976226628588797\\
4	1.35354289111746\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,1.237in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.00167790645812327\\
2	0.00228016548777977\\
3	0.00318742185439004\\
4	0.00462726511721075\\
5	0.00716743728878421\\
6	0.0129273763723776\\
7	0.0308460700090715\\
8	0.115533318647694\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.603245855871981\\
2	0.755456602981771\\
3	0.858512489463287\\
4	0.953124795407537\\
5	1.02704466315581\\
6	1.08592420449446\\
7	1.13090925633169\\
8	1.18526539633296\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,0.481in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
ytick={ 0, 0.4, 0.8},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.000617491691008369\\
2	0.000717776254822589\\
3	0.000835285279992789\\
4	0.000979591082427033\\
5	0.00115487030006212\\
6	0.00136293515999463\\
7	0.00161619354701616\\
8	0.00191279748068678\\
9	0.00227218304658774\\
10	0.0026908090305821\\
11	0.00319938829308565\\
12	0.00381122202979217\\
13	0.00474535479665619\\
14	0.00756353464992525\\
15	0.017474797658002\\
16	0.0547436973724798\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.418853266349202\\
2	0.478839773751748\\
3	0.529812149718329\\
4	0.573539152412764\\
5	0.611663102441733\\
6	0.642886720358442\\
7	0.677359347479036\\
8	0.701877932539796\\
9	0.729554340449397\\
10	0.748421821359951\\
11	0.768367609874633\\
12	0.782658242865203\\
13	0.796571330906253\\
14	0.806933582871612\\
15	0.818312174451126\\
16	0.833414484583038\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

### 2021-03-10 main.tex
:construction: Update manuscript

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
% \usepackage{caption}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[RPvoltages]{circuitikz}
\usepackage[T1]{fontenc}
\usepackage[caption=false,font=footnotesize]{subfig}
% \usepackage[cmintegrals]{newtxmath}
\usepackage[short]{optidef}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/re_subband.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_subband}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/waveform_subband.tex}
			\end{adjustbox}
			\caption{WPT-optimized waveform amplitudes versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:waveform_subband}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/re_distance.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_distance}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/path_loss.tex}
			\end{adjustbox}
			\caption{Path loss versus distance for IEEE TGn channel model D.}
			\label{fi:path_loss}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/re_tx.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_tx}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/re_reflector.tex}
			\end{adjustbox}
			\caption{Average R-E region versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_reflector}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/scaling_tx.tex}
			\end{adjustbox}
			\caption{Average WIT SNR and WPT DC current versus $M$ for $L=20$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_{\mathrm{H}}=0$ and $d_{\mathrm{V}}=0.5\,\si{\meter}$.}
			\label{fi:scaling_tx}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/scaling_reflector.tex}
			\end{adjustbox}
			\caption{Average WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$, $d_{\mathrm{H}}=0$ and $d_{\mathrm{V}}=0.5\,\si{\meter}$.}
			\label{fi:scaling_reflector}
		\end{figure}

		The number of transmit antennas $M$ and IRS elements $L$ influence the average R-E tradeoff as revealed in Fig.~\ref{fi:re_tx} and \ref{fi:re_reflector}. \textit{First,} it is observed that adding either active or passive elements benefits both information and power transmission. This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength. \textit{Second,} the number of active and passive elements have negligible impacts on the optimal transceiving mode (TS/PS). Unlike the noise, the channel strength influences both information and power transfer, thus varying $M$ or $L$ simultaneously scales both rate and current and preserves the general trend of the R-E boundary. \textit{Third,} the passive beamforming has a larger array gain and power scaling order than the active beamforming. This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} that illustrate the performance of WIT and WPT only. For the active MRT beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the average output SNR, corresponding to a transmit array gain of $M$ and a doubled harvester input power. Due to the rectifier nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase, validating the active scaling law in the order of $M^2$ \cite{Clerckx2016a}. On the other hand, when the IRS is very close to the transmitter or the receiver, doubling $L$ can bring an SNR boost up to \SI{6}{\dB}, corresponding to a reflect array gain of $L^2$. An interpretation is that the IRS coherently combines multiple signal copies with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$, achieving a total gain of $L^2$. As a consequence, doubling IRS elements brings a four-fold boost on the received signal power that further amplifies the harvested DC current by \num{16} times (\SI{24}{\dB}), suggesting a passive scaling law in the order of $L^4$. Besides, by considering harvester nonlinearity, the proposed design brings a nearly \SI{20}{\dB} increase in the output DC current over the conventional linear perspective. These results emphasize the effectiveness of passive beamforming and the importance of modeling rectifier nonlinearity in the SWIPT system design. \textit{Fourth,} small-scale SWIPT is dominated by the active beamforming while large-scale SWIPT relies more on the passive beamforming. As shown in Fig.~\ref{fi:path_loss}, in our setup, the direct path loss $\Lambda_\mathrm{D}$ is around \SI{60}{\dB} while the auxiliary path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ is over \SI{100}{\dB}. Hence, to fully exploit the R-E advantage of passive beamforming, a large number of reflecting elements are required to enhance the auxiliary channel strength. Another explanation is that the RF-chains of active antennas provide design flexibility in the frequency domain, while the frequency-flat characteristic of the IRS restricts its benefit for broadband transmission, especially when $L$ is small.
		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/re_irs_1mhz.tex}
			\end{adjustbox}
			\caption{Average R-E region for ideal, adaptive, fixed and no IRS over $B=1\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_irs_1mhz}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\begin{adjustbox}{width=0.9\columnwidth}
				\input{assets/re_irs_10mhz.tex}
			\end{adjustbox}
			\caption{Average R-E region for ideal, adaptive, fixed and no IRS over $B=10\,\si{\MHz}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
			\label{fi:re_irs_10mhz}
		\end{figure}

>>>>

\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{array}
% \usepackage{caption}
\usepackage{cite}
\usepackage{colortbl}
\usepackage{environ}
\usepackage{grffile}
\usepackage{hyperref}
\usepackage{import}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{stfloats}
\usepackage{tikz}
\usepackage{url}
\usepackage{xcolor}
\usepackage[RPvoltages]{circuitikz}
\usepackage[T1]{fontenc}
\usepackage[caption=false,font=footnotesize]{subfig}
% \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
% \usepackage[cmintegrals]{newtxmath}
\usepackage[short]{optidef}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_subband}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_subband.tex}
				}
			}
			\subfloat[Waveform amplitude\label{fi:waveform_subband}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/waveform_subband.tex}
				}
			}
			\caption{Average R-E region and waveform amplitude versus $N$ for $M=1$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_distance}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_distance.tex}
				}
			}
			\subfloat[Path loss\label{fi:path_loss}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/path_loss.tex}
				}
			}
			\caption{Average R-E region and path loss versus $d_{\mathrm{H}}$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{V}}=2\,\si{\meter}$.}
		\end{figure}

@@

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_tx}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_tx.tex}
				}
			}
			\subfloat[WIT SNR and WPT DC current\label{fi:scaling_tx}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/scaling_tx.tex}
				}
			}
			\caption{Average R-E region, WIT SNR and WPT DC current versus $M$ for $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
		\end{figure}

		\begin{figure}[!t]
			\centering
			\subfloat[R-E region\label{fi:re_reflector}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_reflector.tex}
				}
			}
			\subfloat[WIT SNR and WPT DC current\label{fi:scaling_reflector}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/scaling_reflector.tex}
				}
			}
			\caption{Average R-E region, WIT SNR and WPT DC current versus $L$ for $M=1$, $N=16$, $\sigma_n=-40\,\si{\dBm}$, $B=1\,\si{\MHz}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
		\end{figure}

		The number of transmit antennas $M$ and IRS elements $L$ influence the average R-E tradeoff as revealed in Fig.~\ref{fi:re_tx} and \ref{fi:re_reflector}. \textit{First,} it is observed that adding either active or passive elements benefits both information and power transmission. This is because increasing $M$ or $L$ indeed enhances the equivalent composite channel strength. \textit{Second,} the number of active and passive elements have negligible impacts on the optimal transceiving mode (TS/PS). Unlike the noise, the channel strength influences both information and power transfer, thus varying $M$ or $L$ simultaneously scales both rate and current and preserves the general trend of the R-E boundary. \textit{Third,} the passive beamforming has a larger array gain and power scaling order than the active beamforming. This behavior is more obvious in Fig.~\ref{fi:scaling_tx} and \ref{fi:scaling_reflector} that illustrate the performance of WIT and WPT only. For the active MRT beamforming, doubling $M$ brings a \SI{3}{\dB} gain at the average output SNR, corresponding to a transmit array gain of $M$ and a doubled harvester input power. Due to the rectifier nonlinearity, the output DC current ends up with a nearly four-time (\SI{12}{\dB}) increase, validating the active scaling law in the order of $M^2$ \cite{Clerckx2016a}. On the other hand, when the IRS is very close to the transmitter or the receiver, doubling $L$ can bring an SNR boost up to \SI{6}{\dB}, corresponding to a reflect array gain of $L^2$. An interpretation is that the IRS coherently combines multiple signal copies with a receive array gain $L$, then performs an equal gain reflection with a transmit array gain $L$, achieving a total gain of $L^2$. As a consequence, doubling IRS elements brings a four-fold boost on the received signal power that further amplifies the harvested DC current by \num{16} times (\SI{24}{\dB}), suggesting a passive scaling law in the order of $L^4$. Besides, by considering harvester nonlinearity, the proposed design brings a nearly \SI{20}{\dB} increase in the output DC current over the conventional linear perspective. These results emphasize the effectiveness of passive beamforming and the importance of modeling rectifier nonlinearity in the SWIPT system design. \textit{Fourth,} small-scale SWIPT is dominated by the active beamforming while large-scale SWIPT relies more on the passive beamforming. As shown in Fig.~\ref{fi:path_loss}, in our setup, the direct path loss $\Lambda_\mathrm{D}$ is around \SI{60}{\dB} while the auxiliary path loss product $\Lambda_{\mathrm{I}}\Lambda_R$ is over \SI{100}{\dB}. Hence, to fully exploit the R-E advantage of passive beamforming, a large number of reflecting elements are required to enhance the auxiliary channel strength. Another explanation is that the RF-chains of active antennas provide design flexibility in the frequency domain, while the frequency-flat characteristic of the IRS restricts its benefit for broadband transmission, especially when $L$ is small.

		\begin{figure}[!t]
			\centering
			\subfloat[$B=1\,\si{\MHz}$\label{fi:re_irs_1mhz}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_irs_1mhz.tex}
				}
			}
			\subfloat[$B=10\,\si{\MHz}$\label{fi:re_irs_10mhz}]{
				\resizebox{0.45\columnwidth}{!}{
					\input{assets/re_irs_10mhz.tex}
				}
			}
			\caption{Average R-E region for ideal, adaptive, fixed and no IRS versus $B$ for $M=1$, $N=16$, $L=20$, $\sigma_n=-40\,\si{\dBm}$ and $d_{\mathrm{H}}=d_{\mathrm{V}}=2\,\si{\meter}$.}
		\end{figure}
